---
title: "R Notebook"
output:
  html_notebook: default
---

```{r}
library("dplyr")
library("ggplot2")
library("tidyr")
library("reshape")
library("plotly")
library("gganimate")
library("gapminder")
library("av")
library("gifski")
library("ggmap")
library(tmap)    # for static and interactive maps
library(leaflet) # for interactive maps
library(mapview) # for interactive maps
library(shiny)   # for web applications
library(grid)
library(choroplethr)
library(choroplethrMaps)
library(usmap)
```



Per Day reported cases graph across the world
```{r}
'&' <- function(x, y)paste0(x,y)
Date_to_load<-20200419
info <- read.csv ("D:\\Kaggle\\Covid\\latest", stringsAsFactors = T)
info$dateRep<- gsub('-', '/',info$dateRep)
info$dateRep<-as.Date.factor (info$dateRep,format="%d/%m/%Y")
info$countriesAndTerritories<- gsub('United_States_of_America', 'U.S.A.',info$countriesAndTerritories)
info$countriesAndTerritories<- gsub('_', ' ',info$countriesAndTerritories)
info1<-arrange(info, dateRep)%>%group_by(dateRep)%>%summarize(total = sum(cases)/1000)%>%mutate(Cumm_total = cumsum(total))


ggplot(info1,aes(x =dateRep , y = total))+ geom_point(data = info1,color = "red") + geom_line(data = info1,color = "red",size = 1) +ylab("Daily Total Count (in Thousands)")+xlab("Period")+ labs(title="Daily Covid-19 Reported Cases across world")

# ggplot(info1,aes(x =dateRep , y = total, fill=dateRep))+ geom_point(data = info1) + geom_smooth(method = "loess") +ylab("Daily Total Count (in Thousands)")+xlab("Period")+ labs(title="Daily Covid-19 Reported Cases across world")+ geom_density2d()

#  plot_ly(
#   type='scatter',
#   mode='markers',
#   x=info1$dateRep,
#   y=info1$total,
#   name="Daily Reported cases"
# )
```

Cummulative frequency across the world. We can see difference between the dots increasing which means frequency is increasing 
```{r}
ggplot(info1,aes(x =dateRep , y = as.integer(Cumm_total)))+ geom_point(data = info1,color = "red") + geom_line(data = info1,color = "red",size = 1) +ylab("Cummulative Total  (in Thousands)")+xlab("Period")+xlab("Period")+ labs(title="Cummulative reported cases across the world")
```


```{r}

info1<-arrange(info, dateRep)%>%group_by(dateRep)%>%summarize(total = sum(deaths))%>%mutate(Cumm_total = cumsum(total))
ggplot(info1,aes(x =dateRep , y = total))+ geom_point(data = info1,colour = "red") + geom_line(data = info1,color = "red",size = 1) +ylab("Daily Death Count")+xlab("Period")+xlab("Period")+ labs(title="Daily Covid-19 Reported Deaths across world")

```

```{r}
ggplot(info1,aes(x =dateRep , y = as.integer(Cumm_total)))+ geom_point(data = info1,color = "red") + geom_line(data = info1,color = "red",size = 1) +ylab("Total Deaths Count")+xlab("Period")+xlab("Period")+ labs(title="Cummulative Reported Deaths across the world")
```

It has already reached in 192 Countries. 
```{r}
#info1<-data.frame(unique(info$countriesAndTerritories))    #Distinct Countries
info1<-info%>%group_by(countriesAndTerritories)%>%summarize(total_cases = sum(cases), total_pop = max(popData2018), total_deaths=sum(deaths))

info2<-top_n(info1,15,total_cases)
info2$total_cases<-(info2$total_cases/1000)
ggplot(info2,aes(x =countriesAndTerritories, y = total_cases, fill="red"))+ geom_col() + theme(axis.text.x=element_text(size=15, angle=90, hjust = 1, vjust = 0.5)) +xlab("Countries")+ylab("Total Cases Reported (in thousands)")+ labs(title="Countries with highest number of Covid-19 Cases")
```


```{r}
info2<-top_n(info1,15,total_deaths)
ggplot(info2,aes(x =countriesAndTerritories, y = total_deaths, fill="red"))+ geom_col() + theme(axis.text.x=element_text(size=15, angle=90, hjust = 1, vjust = 0.5 ))+xlab("Countries")+ylab("Total Deaths Reported")+ labs(title="Countries with highest number of Deaths")
```

```{r}

info1[,"Cases_to_Popuation_Pct"]<-(info1$total_cases/info1$total_pop)*100
info2<-filter(info1,total_cases>1000)%>% top_n(15,Cases_to_Popuation_Pct)
ggplot(info2,aes(x =countriesAndTerritories, y = Cases_to_Popuation_Pct, fill="red"))+ geom_col() + theme(axis.text.x=element_text(size=15, angle=90, hjust = 1, vjust = 0.5 ))+xlab("Countries")+ylab("Percentage of Cases Reported to Total Popultion")+ labs(title="Countries with highest number of cases w.r.t. population")
```


```{r}
info1[,"Deaths_to_Cases_Pct"]<-(info1$total_deaths/info1$total_cases)*100
info2<-filter(info1,total_cases>1000)%>%top_n(15,Deaths_to_Cases_Pct)
ggplot(info2,aes(x =countriesAndTerritories, y = Deaths_to_Cases_Pct, fill="red"))+ geom_col() + theme(axis.text.x=element_text(size=15, angle=90, hjust = 1, vjust = 0.5 ))+xlab("Countries")+ylab("Percentage of Deaths Reported to Total Cases")+ labs(title="Countries with highest number of Deaths w.r.t. Total Cases")
```

Counties with highest number of cases
```{r}
info2<-top_n(info1,6,total_cases)
info2<-inner_join(info, info2,"countriesAndTerritories")
t<-ggplot(info2,aes(x =dateRep , y = cases, color=countriesAndTerritories)) + geom_point() + geom_line() + ylab("Cases Per Day")+xlab("Period")+ labs(title="Countries with Highest number of Cases - Daily Count of reported cases")
t+facet_wrap(~countriesAndTerritories) + guides(fill="none")
```
Counties with highest number of deaths
```{r}
info2<-top_n(info1,6,total_deaths)
info2<-inner_join(info, info2,"countriesAndTerritories")
t<-ggplot(info2,aes(x =dateRep , y = deaths, color=countriesAndTerritories)) + geom_point() + geom_line() + ylab("Deaths Per Day")+xlab("Period")+ labs(title="Countries with Highest number of Deaths Daily Count")
t+facet_wrap(~countriesAndTerritories)

```
World view ---------------- should not delete
```{r}

info2<-arrange(info, countriesAndTerritories,dateRep)%>%group_by(countriesAndTerritories,dateRep)%>%summarize(total_cases = sum(cases),total_deaths = sum(deaths))%>%mutate(Cumm_total_cases = cumsum(total_cases),Cumm_total_deaths = cumsum(total_deaths))
info1[,"category"]<-ifelse(info1$countriesAndTerritories == "China","Recovering",
                          ifelse(info1$countriesAndTerritories == "South Korea", "Recovering",
                                 ifelse(info1$total_cases>=10000,">= 10000","< 10000")))
info2<-inner_join(info1,info2,"countriesAndTerritories")
t<-ggplot(info2,aes(x =dateRep , y = Cumm_total_cases, color=category)) + geom_point() + geom_line() + ylab("Total Cases")+xlab("Period")+ labs(title="All Countries Data")+scale_color_manual(values=c('blue','red','green'))
t+facet_wrap(~countriesAndTerritories)

```
How it started for the coutries in red

```{r}

# info3<-filter(info2,category==">= 10000")
# 
# p<-ggplot(info3, aes(Cumm_total_deaths,Cumm_total_cases , size = Cumm_total_cases, colour = countriesAndTerritories)) +
#   geom_point(alpha = 0.7, show.legend = FALSE) +
#   scale_colour_manual(values = c("green","blue","red","brown","black","orange","yellow","maroon")) +
#   scale_size(range = c(2, 12)) +
#   scale_x_log10() +
#   facet_wrap(~countriesAndTerritories) +
#   # Here comes the gganimate specific bits
#   labs(title = 'Day: {frame_time}', x = 'Deaths', y = 'Cases') +
#   transition_time(info3$dateRep) +
#   ease_aes('linear')
# 
# animate(p, nframes = 100, fps=3)


```



Highest number of cases reported today
```{r}
info1<-filter(info,dateRep<as.Date.character(Date_to_load,format = "%Y%m%d"))%>%group_by(countriesAndTerritories)%>%summarize(total_cases = sum(cases), total_pop = max(popData2018), total_deaths=sum(deaths))
info2<-filter(info,dateRep==as.Date.character(Date_to_load,format = "%Y%m%d"))%>%top_n(15,cases)
info2<-inner_join(info1,info2,"countriesAndTerritories")
fig <- plot_ly(info2, x = ~countriesAndTerritories, y = ~total_cases, type = 'bar',name='Total Till Yesterday',text = ~total_cases, textposition = 'auto')

Date_to_load1<-as.Date.character(Date_to_load,format = "%Y%m%d")
fig <- fig %>% add_trace(y = ~cases,name = 'Cases Reported Today',text = ~cases , textposition = 'auto')
fig <- fig %>% layout(title = "Countries with Highest number of cases reported today ("&Date_to_load1&")", xaxis = list(title = 'Countries'), yaxis = list(title = 'Cases Count'), barmode = 'stack')

fig

```

Highest number of deaths reported today
```{r}
info2<-filter(info,dateRep==as.Date.character(Date_to_load,format = "%Y%m%d"))%>%top_n(15,deaths)
info2<-inner_join(info1,info2,"countriesAndTerritories")
fig <- plot_ly(info2, x = ~countriesAndTerritories, y = ~total_deaths, type = 'bar',name='Total Deaths Till Yesterday',text = ~total_deaths, textposition = 'auto')
Date_to_load1<-as.Date.character(Date_to_load,format = "%Y%m%d")
fig <- fig %>% add_trace(y = ~deaths,name = 'Deaths Reported Today',text = ~deaths , textposition = 'auto')
fig <- fig %>% layout(title = "Countries with Highest number of deaths reported today ("&Date_to_load1&")", xaxis = list(title = 'Countries'),yaxis = list(title = 'Death Count'), barmode = 'stack')

fig
```
Country specific data
```{r}

country<-"India"
info2<-filter(info,countriesAndTerritories==country)%>%arrange(dateRep)%>%group_by(dateRep)%>%summarize(total_cases = sum(cases),total_deaths = sum(deaths))%>%mutate(Cumm_total_cases = cumsum(total_cases),Cumm_total_deaths = cumsum(total_deaths))


fig <- plot_ly(info2, x = ~dateRep, y = ~Cumm_total_cases, name = 'Total Cases', type = 'scatter', mode = 'lines+markers') 
fig <- fig %>% add_trace(y = ~Cumm_total_deaths, name = 'Total Deaths', mode = 'lines+markers') 
fig <-fig %>% layout(title = country&" Data today ("&Date_to_load1&")", xaxis = list(title = 'Period'),yaxis = list(title = 'Count'))
fig
# ggplot() + 
#   geom_line(data = info2, aes(x = dateRep, y = Cumm_total_cases), color = "red") +
#   geom_point(data = info2, aes(x = dateRep, y = Cumm_total_cases), color = "red")+
#   geom_line(data = info2, aes(x = dateRep, y = Cumm_total_deaths), color = "blue") +
#   geom_point(data = info2, aes(x = dateRep, y = Cumm_total_deaths), color = "blue")+
#   xlab('Period') +
#   ylab('Total Count') +
#   labs(title=country&" Data")
```

Github_recovery_data
```{r}
covid_recovery <- read.csv ("D:\\Kaggle\\Covid\\Recovery_Data\\time_Series_recovered", stringsAsFactors = F)
covid_recovery <- melt(covid_recovery, id=c("Province.State","Country.Region","Lat","Long"),variable_name = "dateRep")
names(covid_recovery)[names(covid_recovery) == "value"] <- "total"
covid_recovery$dateRep<- gsub('X', '0',covid_recovery$dateRep)
covid_recovery$dateRep<-as.Date.factor (covid_recovery$dateRep,format="%m.%d.%y")

covid_deaths <- read.csv ("D:\\Kaggle\\Covid\\Recovery_Data\\time_series_deaths", stringsAsFactors = F)
covid_deaths <- melt(covid_deaths, id=c("Province.State","Country.Region","Lat","Long"),variable_name = "dateRep")
names(covid_deaths)[names(covid_deaths) == "value"] <- "total"
covid_deaths$dateRep<- gsub('X', '0',covid_deaths$dateRep)
covid_deaths$dateRep<-as.Date.factor (covid_deaths$dateRep,format="%m.%d.%y")

covid_confirmed <- read.csv ("D:\\Kaggle\\Covid\\Recovery_Data\\time_Series_confirmed", stringsAsFactors = F)
covid_confirmed <- melt(covid_confirmed, id=c("Province.State","Country.Region","Lat","Long"),variable_name = "dateRep")
names(covid_confirmed)[names(covid_confirmed) == "value"] <- "total"
covid_confirmed$dateRep<- gsub('X', '0',covid_confirmed$dateRep)
covid_confirmed$dateRep<-as.Date.factor (covid_confirmed$dateRep,format="%m.%d.%y")

covid_recovery[,"type"]<-"Recovered"
covid_deaths[,"type"]<-"Deaths"
covid_confirmed[,"type"]<-"Total_Cases"
total_world_info<-rbind(covid_recovery,covid_deaths)
total_world_info<-rbind(total_world_info,covid_confirmed)
total_world_info<-filter(total_world_info,total_world_info$Province.State!="Recovered")
```


```{r}
# covid_recovery_info<-covid_recovery%>%group_by(dateRep)%>%summarize(total_recovered_world = sum(total_recovered)/1000)
# covid_deaths_info<-covid_deaths%>%group_by(dateRep)%>%summarize(total_deaths_world = sum(total_deaths)/1000)
# covid_confirmed_info<-covid_confirmed%>%group_by(dateRep)%>%summarize(total_confirmed_world = sum(total_cases)/1000)

total_world_info1<-arrange(total_world_info, type,dateRep)%>%group_by(type,dateRep)%>%summarize(total_type_date = sum(total)/1000)

# covid_recovery_info[,"type"]<-"recovered"
# covid_deaths_info<-covid_deaths%>%group_by(dateRep)%>%summarize(total = sum(total_deaths)/1000)
# covid_deaths_info[,"type"]<-"deaths"
# covid_confirmed_info<-covid_confirmed%>%group_by(dateRep)%>%summarize(total = sum(total_cases)/1000)
# covid_confirmed_info[,"type"]<-"confirmed"
# 
# total_world<-rbind(covid_recovery_info,covid_deaths_info)
# total_world<-rbind(total_world,covid_confirmed_info)

# ggplot() +
#   geom_line(data =subset(total_world,type=="recovered"), aes(x = dateRep, y = total),size=1, colour='green' )+
#   geom_point(data = subset(total_world,type=="recovered"), aes(x = dateRep, y = total), colour = 'green')+
#   geom_line(data = subset(total_world,type=="deaths"), aes(x = dateRep, y = total),size=1,colour='red') +
#   geom_point( data = subset(total_world,type=="deaths"), aes(x = dateRep, y = total),colour='red')+
#   geom_line(data = subset(total_world,type=="confirmed"), aes(x = dateRep, y = total), size=1,colour='orange') +
#   geom_point(data = subset(total_world,type=="confirmed"), aes(x = dateRep, y = total),colour='orange')+
#   xlab('Period') +
#   ylab('Total Count (in thousands)') +
#   labs(title="World Data For Case, Recovery and Deaths") + theme_bw() +guides

ggplot(total_world_info1, mapping=aes(x=dateRep, y=total_type_date)) + geom_line(mapping=aes(colour=type),size=1) + geom_point(mapping=aes(colour=type))+labs(title="World Data For Case, Recovery and Deaths") + theme_bw() +scale_color_hue("Line Type")+xlab('Period') +
  ylab('Total Count (in thousands)')+scale_color_manual(
  values=c("red", "green","orange"))



```

Rest of world
```{r}


total_world_info1<-filter(total_world_info,Country.Region!="China")

total_world_info1<-arrange(total_world_info1, type,dateRep)%>%group_by(type,dateRep)%>%summarize(total_type_date = sum(total)/1000)


# ggplot() +
#   geom_line(data =subset(total_world,type=="recovered"), aes(x = dateRep, y = total),size=1, colour='green' )+
#   geom_point(data = subset(total_world,type=="recovered"), aes(x = dateRep, y = total), colour = 'green')+
#   geom_line(data = subset(total_world,type=="deaths"), aes(x = dateRep, y = total),size=1,colour='red') +
#   geom_point( data = subset(total_world,type=="deaths"), aes(x = dateRep, y = total),colour='red')+
#   geom_line(data = subset(total_world,type=="confirmed"), aes(x = dateRep, y = total), size=1,colour='orange') +
#   geom_point(data = subset(total_world,type=="confirmed"), aes(x = dateRep, y = total),colour='orange')+
#   xlab('Period') +
#   ylab('Total Count (in thousands)') +
#   labs(title="World Data For Case, Recovery and Deaths") + theme_bw() +guides

ggplot(total_world_info1, mapping=aes(x=dateRep, y=total_type_date)) + geom_line(mapping=aes(colour=type),size=1) + geom_point(mapping=aes(colour=type))+labs(title="World Data For Case, Recovery and Deaths") + theme_bw() +scale_color_hue("Line Type")+xlab('Period') +
  ylab('Total Count (in thousands)')+scale_color_manual(
  values=c("red", "green","orange"))
```
Country Specific

```{r}


country_filter <- c("Germany","Spain","Italy","Iran","France","US","India")

total_world_info1<-filter(total_world_info,Country.Region%in%country_filter)

total_world_info1<-arrange(total_world_info1, type,dateRep)%>%group_by(Country.Region,type,dateRep)%>%summarize(total_type_date = sum(total)/1000)




# ggplot() +
#   geom_line(data =subset(total_world,type=="recovered"), aes(x = dateRep, y = total),size=1, colour='green' )+
#   geom_point(data = subset(total_world,type=="recovered"), aes(x = dateRep, y = total), colour = 'green')+
#   geom_line(data = subset(total_world,type=="deaths"), aes(x = dateRep, y = total),size=1,colour='red') +
#   geom_point( data = subset(total_world,type=="deaths"), aes(x = dateRep, y = total),colour='red')+
#   geom_line(data = subset(total_world,type=="confirmed"), aes(x = dateRep, y = total), size=1,colour='orange') +
#   geom_point(data = subset(total_world,type=="confirmed"), aes(x = dateRep, y = total),colour='orange')+
#   xlab('Period') +
#   ylab('Total Count (in thousands)') +
#   labs(title="World Data For Case, Recovery and Deaths") + theme_bw() +guides

ggplot(total_world_info1, mapping=aes(x=dateRep, y=total_type_date)) + geom_line(mapping=aes(colour=type),size=1) + geom_point(mapping=aes(colour=type))+labs(title="Data For Case, Recovery and Deaths") + theme_bw() +scale_color_hue("Line Type")+xlab('Period') +
  ylab('Total Count (in thousands)')+scale_color_manual(
  values=c("red", "green","orange"))+facet_wrap(~Country.Region)


```


Country Specific
```{r}
country_filter = "India"

total_world_info1<-filter(total_world_info,Country.Region==country_filter)

total_world_info1<-arrange(total_world_info1, type,dateRep)%>%group_by(type,dateRep)%>%summarize(total_type_date = sum(total))

# ggplot() +
#   geom_line(data =subset(total_world,type=="recovered"), aes(x = dateRep, y = total),size=1, colour='green' )+
#   geom_point(data = subset(total_world,type=="recovered"), aes(x = dateRep, y = total), colour = 'green')+
#   geom_line(data = subset(total_world,type=="deaths"), aes(x = dateRep, y = total),size=1,colour='red') +
#   geom_point( data = subset(total_world,type=="deaths"), aes(x = dateRep, y = total),colour='red')+
#   geom_line(data = subset(total_world,type=="confirmed"), aes(x = dateRep, y = total), size=1,colour='orange') +
#   geom_point(data = subset(total_world,type=="confirmed"), aes(x = dateRep, y = total),colour='orange')+
#   xlab('Period') +
#   ylab('Total Count (in thousands)') +
#   labs(title="World Data For Case, Recovery and Deaths") + theme_bw() +guides

ggplot(total_world_info1, mapping=aes(x=dateRep, y=total_type_date)) + geom_line(mapping=aes(colour=type),size=1) + geom_point(mapping=aes(colour=type))+labs(title=country_filter&" Data For Case, Recovery and Deaths") + theme_bw() +scale_color_hue("Line Type")+xlab('Period') +
  ylab('Total Count')+scale_color_manual(
  values=c("red", "green","orange"))

```
Top Countries who recovered
```{r}
Date_to_load<-"20200419"
Date_to_load1<-as.Date.character(Date_to_load,format = "%Y%m%d")
total_world_info1<-filter(total_world_info,type=="Recovered")%>%group_by(Country.Region,dateRep)%>%summarize(total_recovered = sum(total))%>%filter( dateRep==as.Date.character(Date_to_load,format = "%Y%m%d"))

total_world_info2<-top_n(as.data.frame(total_world_info1),15,total_recovered)
total_world_info2$Country.Region<-as.character(total_world_info2$Country.Region)

fig <- plot_ly(total_world_info2, x = total_world_info2$Country.Region, y = ~total_recovered, type = 'bar',name='Total Recovered',text = ~total_recovered, textposition = 'auto')

#fig <- fig %>% add_trace(y= ~total_recovered,name = 'Cases Recovered Today',text = ~total_recovered , textposition = 'auto')
fig <- fig %>% layout(title = "Countries with Highest number of recovered till date ("&Date_to_load1&")", xaxis = list(title = 'Countries'),yaxis = list(title = 'Recover Count'))

fig


```
countries with highest recovery today

```{r}
total_world_info3<-filter(total_world_info,type=="Recovered")%>%group_by(Country.Region,dateRep)%>%summarize(total_recovered = sum(total))%>%filter( dateRep==as.Date.character(Date_to_load,format = "%Y%m%d")-1)

total_world_info3<-left_join(total_world_info1,total_world_info3,by="Country.Region")

total_world_info3[,"recovered_today"]<-total_world_info3$total_recovered.x-total_world_info3$total_recovered.y

total_world_info3<-top_n(as.data.frame(total_world_info3),15,recovered_today)
total_world_info3$Country.Region<-as.character(total_world_info3$Country.Region)

fig <- plot_ly(total_world_info3, x = ~Country.Region, y = ~total_recovered.y, type = 'bar',name='Total Recovered till yesterday',text = ~total_recovered.y, textposition = 'auto')

fig <- fig %>% add_trace(y= ~recovered_today,name = 'Cases Recovered Today',text = ~recovered_today , textposition = 'auto')
fig <- fig %>% layout(title = "Countries with Highest number of recovered today ("&Date_to_load1&")", xaxis = list(title = 'Countries'),yaxis = list(title = 'Recover Count'), barmode = 'stack')

fig
```
countries with best recovery rate
```{r}
total_world_info1<-arrange(total_world_info, Country.Region,type,dateRep)%>%group_by(Country.Region,type,dateRep)%>%summarize(total_country_type_date = sum(total))


total_world_info2<-filter(total_world_info1,type=="Total_Cases")%>%filter(total_country_type_date >0)%>%group_by(Country.Region)%>%summarize(first_date_case = min(total_country_type_date),dateRep=min(dateRep))

total_world_info2[,"days_from_first_case"]<-(as.Date.character(Date_to_load,format = "%Y%m%d") - total_world_info2$dateRep)
total_world_info3<-filter(total_world_info1,dateRep==as.Date.character(Date_to_load,format = "%Y%m%d"))
total_world_info3<-inner_join(total_world_info3,total_world_info2,"Country.Region")
total_world_info3[,"rate"]<-round((total_world_info3$total_country_type_date)/as.numeric(total_world_info3$days_from_first_case),0)
total_world_info2<-filter(total_world_info3,type=="Recovered")%>%filter(Country.Region!="China")%>%filter(Country.Region!="Korea, South")
total_world_info2<-top_n(as.data.frame(total_world_info2),15,rate)
total_world_info2<-inner_join(filter(total_world_info3,type=="Total_Cases"),total_world_info2,"Country.Region")

fig <- plot_ly(total_world_info2, x = ~Country.Region, y = ~rate.x, type = 'bar',name='Case Rate (Average New Cases per Day)',text = ~rate.x, textposition = 'auto')
fig <- fig %>% add_trace(y= ~rate.y,name = 'Recovery Rate (Average People recovered per day)',text = ~rate.y , textposition = 'auto')
fig <- fig %>% layout(title = "Countries Recovery/Case rate. Average take starting first case appeared in that country  ("&Date_to_load1&")", xaxis = list(title = 'Countries with highest recovery rate per day '),yaxis = list(title = 'Average Case/Recovered Per day'))

fig

```
case and recovery rate with population density

```{r}

total_world_info1<-arrange(total_world_info, Country.Region,type,dateRep)%>%group_by(Country.Region,type,dateRep)%>%summarize(total_country_type_date = sum(total))


total_world_info2<-filter(total_world_info1,type=="Total_Cases")%>%filter(total_country_type_date >0)%>%group_by(Country.Region)%>%summarize(first_date_case = min(total_country_type_date),dateRep=min(dateRep))

total_world_info2[,"days_from_first_case"]<-(as.Date.character(Date_to_load,format = "%Y%m%d") - total_world_info2$dateRep)
total_world_info3<-filter(total_world_info1,dateRep==as.Date.character(Date_to_load,format = "%Y%m%d"))
total_world_info3<-inner_join(total_world_info3,total_world_info2,"Country.Region")
total_world_info3[,"rate"]<-round((total_world_info3$total_country_type_date)/as.numeric(total_world_info3$days_from_first_case),0)
total_world_info2<-filter(total_world_info3,type=="Total_Cases")%>%filter(Country.Region!="China")
total_world_info2<-inner_join(filter(total_world_info3,type=="Recovered"),total_world_info2,"Country.Region")
total_world_info2[,"pct_avg_recovered_to_avg_cases"]<-round((total_world_info2$rate.x/total_world_info2$rate.y)*100,2)

pop_density <- read.csv ("D:\\Kaggle\\Covid\\API_EN.POP.DNST_DS2_en_csv_v2_887474\\pop_desity.csv", stringsAsFactors = F)


total_world_info2<-inner_join(filter(total_world_info2,total_country_type_date.y>1000),pop_density,c("Country.Region" = "Country_Name"))

total_world_info3<-top_n(as.data.frame(total_world_info2),15,pct_avg_recovered_to_avg_cases)

fig <- plot_ly(total_world_info3, x = ~Country.Region, y = ~pct_avg_recovered_to_avg_cases, type = 'bar',name='Avg Recovery Percentge w.r.t. Avg Cases',text = ~pct_avg_recovered_to_avg_cases, textposition = 'auto')

fig <- fig %>% layout(title = "Countries with more than 1000 cases and highest recovery percentage ("&Date_to_load1&")", xaxis = list(title = 'Countries'),yaxis = list(title = 'Percentage'))

fig1 <- plot_ly(total_world_info3,y= ~popdensity,x = ~Country.Region,name = 'Population Density of the Country(people per sq. km of land area)',text =~round(popdensity,2) , textposition = 'auto')


figplot1<-subplot(fig,fig1,nrows = 2, shareX = T)

total_world_info2<-filter(total_world_info2,total_country_type_date.x>0)
total_world_info4<-top_n(as.data.frame(total_world_info2),-15,pct_avg_recovered_to_avg_cases)


fig <- plot_ly(total_world_info4, x = ~Country.Region, y = ~pct_avg_recovered_to_avg_cases, type = 'bar',name='Avg Recovery Percentge w.r.t. Avg Cases',text = ~pct_avg_recovered_to_avg_cases, textposition = 'auto')

fig <- fig %>% layout(title = "Countries with more than 1000 cases and lowest recovery percentage ("&Date_to_load1&")", xaxis = list(title = 'Countries'),yaxis = list(title = 'Percentage'))

fig1 <- plot_ly(total_world_info4,y= ~popdensity,x = ~Country.Region,name = 'Population Density of the Country(people per sq. km of land area)',text =~round(popdensity,2) , textposition = 'auto')

figplot2<-subplot(fig,fig1,nrows = 2, shareX = T)

figplot<-subplot(figplot1,figplot2)

# 
# 
# total_world_info1<-arrange(total_world_info, Country.Region,type,dateRep)%>%group_by(Country.Region,type,dateRep)%>%summarize(total_country_type_date = sum(total))%>%filter(type=="Total_Cases")%>%filter(dateRep==as.Date.character(Date_to_load,format = "%Y%m%d"))%>%filter(total_country_type_date >1000)
# 
# total_world_info1<-inner_join(total_world_info1,pop_density,c("Country.Region" = "Country_Name"))
# total_world_info1<-top_n(as.data.frame(total_world_info1),15,popdensity)
# 
# fig3 <- plot_ly(total_world_info1,y= ~popdensity,x = ~Country.Region,name = 'Countries where population density is highest (people per sq. km of land area)',text =~round(popdensity,2) , textposition = 'auto')


figplot



```





Total showing all 3 metrics in bar graph

```{r}
total_world_info1<-arrange(total_world_info, Country.Region,type,dateRep)%>%group_by(Country.Region,type,dateRep)%>%summarize(total_country_type_date = sum(total)) %>%filter(dateRep==as.Date.character(Date_to_load,format = "%Y%m%d"))

total_world_info2<-total_world_info1 %>% filter(type == "Total_Cases")

total_world_info2<-top_n(as.data.frame(total_world_info2),15,total_country_type_date)

total_world_info2<-inner_join(total_world_info1,total_world_info2,by="Country.Region")

total_world_info3<-filter(total_world_info2,type.x =="Recovered" || type.x =="Deaths")%>%group_by(Country.Region,dateRep.x)%>%summarize(rec_death=(sum(total_country_type_date.x)))

total_world_info3<-filter(total_world_info2,type.x=="Total_Cases")%>%inner_join(total_world_info3,by=c("Country.Region","dateRep.x"))
total_world_info3[,"Active_Cases"]<-total_world_info3$total_country_type_date.x-total_world_info3$rec_death

fig <- plot_ly(data=total_world_info3, x = ~Country.Region, y = ~Active_Cases, type = 'bar',name='Total Active Cases',text = ~Active_Cases, textposition = 'auto')

fig <- fig %>% add_trace(data=subset(total_world_info2,type.x=="Deaths"), y= ~total_country_type_date.x,name = 'Deaths',text = ~total_country_type_date.x , textposition = 'auto')

fig <- fig %>% add_trace(data=subset(total_world_info2,type.x=="Recovered"), y= ~total_country_type_date.x,name = 'Cases Recovered',text = ~total_country_type_date.x , textposition = 'auto')

fig <- fig %>% layout(title = "Countries with Highest number of cases ("&Date_to_load1&")", xaxis = list(title = 'Countries'),yaxis = list(title = 'Count'), barmode = 'stack')

fig






```

US Specific Analysis-----------------------------------------------------------------------------------------------

```{r}
us_covid_Confirmed <- read.csv ("D:\\Kaggle\\Covid\\US_SPECIFIC\\US_CONFIRMED", stringsAsFactors = F)
column_count<-length(names(us_covid_Confirmed))
us_covid_Confirmed<-us_covid_Confirmed[,c(5,7,9,10,12:column_count)]
us_covid_Confirmed <- melt(us_covid_Confirmed, id=c("FIPS","Province_State","Lat","Long_"),variable_name = "dateRep")
names(us_covid_Confirmed)[names(us_covid_Confirmed) == "value"] <- "total"
us_covid_Confirmed$dateRep<- gsub('X', '0',us_covid_Confirmed$dateRep)
us_covid_Confirmed$dateRep<-as.Date.factor (us_covid_Confirmed$dateRep,format="%m.%d.%y")

us_covid_deaths <- read.csv ("D:\\Kaggle\\Covid\\US_SPECIFIC\\US_DEATHS", stringsAsFactors = F)
column_count<-length(names(us_covid_deaths))
us_covid_deaths<-us_covid_deaths[,c(5,7,9,10,12:column_count)]
us_covid_deaths <- melt(us_covid_deaths, id=c("FIPS","Province_State","Lat","Long_","Population"),variable_name = "dateRep")
names(us_covid_deaths)[names(us_covid_deaths) == "value"] <- "total"
us_covid_deaths$dateRep<- gsub('X', '0',us_covid_deaths$dateRep)
us_covid_deaths$dateRep<-as.Date.factor (us_covid_deaths$dateRep,format="%m.%d.%y")

FIPS <- read.csv ("D:\\Kaggle\\Covid\\US_SPECIFIC\\FIPS", stringsAsFactors = F)
FIPS<-filter(FIPS,Country_Region=="US")

```


Graph of top 6 states with cases
```{r}

us_covid_Confirmed1<-filter(us_covid_Confirmed)%>%group_by(Province_State,dateRep)%>%summarize(total = sum(total))
us_covid_Confirmed1<-arrange(us_covid_Confirmed1,dateRep)%>%group_by(Province_State)%>%mutate(per_day = c(0,diff(total)))

us_covid_Confirmed2<-us_covid_Confirmed1%>%group_by(Province_State)%>%summarize(total = sum(total))%>%top_n(12,total)
us_covid_Confirmed1<-inner_join(us_covid_Confirmed1,us_covid_Confirmed2,"Province_State")


# ggplot(us_covid_Confirmed1,aes(x=dateRep,y=per_day,fill=Province_State))+geom_smooth(aes(color=Province_State))+geom_point(alpha=0.5,aes(color=Province_State)) + geom_density2d()+facet_wrap(~Province_State)

ggplot(us_covid_Confirmed1,aes(x=dateRep,y=per_day))+geom_point(color="violetred4")+facet_wrap(~Province_State)+geom_smooth(method="loess",color="dodgerblue1",se=F)+theme_bw()+xlab("Period")+ylab("Cases Per Day")+labs(title="US States with highest number of cases")


```
bottom 10 states
```{r}

us_covid_Confirmed1<-filter(us_covid_Confirmed)%>%group_by(Province_State,dateRep)%>%summarize(total = sum(total))
us_covid_Confirmed1<-arrange(us_covid_Confirmed1,dateRep)%>%group_by(Province_State)%>%mutate(per_day = c(0,diff(total)))

us_covid_Confirmed2<-us_covid_Confirmed1%>%group_by(Province_State)%>%summarize(total = sum(total))%>%top_n(-10,total)
us_covid_Confirmed1<-inner_join(us_covid_Confirmed1,us_covid_Confirmed2,"Province_State")


ggplot(us_covid_Confirmed1,aes(x=dateRep,y=per_day,fill=Province_State))+geom_smooth(method = "loess",aes(color=Province_State))+geom_point(alpha=0.5,aes(color=Province_State))+stat_smooth()


```




When first case came for every state in US
```{r}
# 


# us_covid_Confirmed1<-filter(us_covid_Confirmed)%>%group_by(Province_State,dateRep)%>%summarize(total = sum(total))
# us_covid_Confirmed1[,"value"]<-ifelse( us_covid_Confirmed1$total>0 ,1,0)
# 
# 
# 
# statepop<-as.data.frame(statepop)
# 
# us_covid_Confirmed1<-inner_join(us_covid_Confirmed1,statepop,by=c("Province_State"="full"))
# 
#  start_date<-min(us_covid_Confirmed1$dateRep)
#  range<-max(us_covid_Confirmed1$dateRep)-min(us_covid_Confirmed1$dateRep)
# 
#  for (i in 1:range)
#  {
#    p<-plot_usmap(data = filter(us_covid_Confirmed1,dateRep==start_date+i), values = "value", color = "red") +
#    scale_fill_continuous(
#      low = "white", high = "red", name = "1st Case Reported", label = scales::comma
#    ) + labs(title="US States. Date : "&start_date+i)
# 
#      ggsave(
#     filename = "map"&i&".png",
#     plot = p,
#     scale = 1,
#     dpi = 100,
#     width = 10, height = 10
#   )
#  }
# 
# 
# system("magick -delay 80 example_1.gif *.png example_2.gif")
# 





```


How total us cases look on Map
```{r}
data(continental_us_states)


us_covid_Confirmed1<-as.data.frame(filter(us_covid_Confirmed,us_covid_Confirmed$dateRep==Date_to_load1))%>%group_by(Province_State)%>%summarize(value = sum(total))

names(us_covid_Confirmed1)[names(us_covid_Confirmed1)=="Province_State"]<-"region"
us_covid_Confirmed1$region<-tolower(us_covid_Confirmed1$region)

state_choropleth(us_covid_Confirmed1, 
                 num_colors=9,
                 zoom = continental_us_states) +
  scale_fill_brewer(palette="YlOrBr") +
  labs(title = "Statewise Cases in US",
       subtitle = "Covid19 cases",
      # caption = "source: https://en.wikipedia.org/wiki/List_of_U.S._states_by_Hispanic_and_Latino_population",
       fill = "Percent") 


#for (i in us_covid_Confirmed1$dateRep) {
#qmplot(Long_, Lat, data = us_covid_Confirmed1, colour = I('red'), size = I(0.5), darken = .1,source="osm")

#}




```

Deaths in US

```{r}

us_covid_deaths1<-as.data.frame(filter(us_covid_deaths,us_covid_deaths$dateRep==Date_to_load1))%>%group_by(Province_State)%>%summarize(value = sum(total))

names(us_covid_deaths1)[names(us_covid_deaths1)=="Province_State"]<-"region"
us_covid_deaths1$region<-tolower(us_covid_deaths1$region)

state_choropleth(us_covid_deaths1, 
                 num_colors=9,
                 zoom = continental_us_states) +
  scale_fill_brewer(palette="YlOrBr") +
  labs(title = "Statewise Deaths in US",
       subtitle = "Covid19 Deaths",
      # caption = "source: https://en.wikipedia.org/wiki/List_of_U.S._states_by_Hispanic_and_Latino_population",
       fill = "Percent") 

```
population in US
```{r}
us_covid_deaths1<-as.data.frame(filter(us_covid_deaths,us_covid_deaths$dateRep==Date_to_load1))%>%group_by(Province_State)%>%summarize(value = sum(Population))

sum(us_covid_deaths1$value)

names(us_covid_deaths1)[names(us_covid_deaths1)=="Province_State"]<-"region"
us_covid_deaths1$region<-tolower(us_covid_deaths1$region)

state_choropleth(us_covid_deaths1, 
                 num_colors=9,
                 zoom = continental_us_states) +
  scale_fill_brewer(palette="YlOrBr") +
  labs(title = "Statewise Deaths in US",
       subtitle = "Covid19 Deaths",
      # caption = "source: https://en.wikipedia.org/wiki/List_of_U.S._states_by_Hispanic_and_Latino_population",
       fill = "Percent") 


```



How data Deaths look on Map

```{r}
us_covid_deaths1<-as.data.frame(filter(us_covid_deaths,us_covid_deaths$dateRep==Date_to_load1))%>%filter(total>0)


qmplot(Long_, Lat, data = us_covid_deaths1, colour = I('red'), size = I(0.5), darken = .1, legend = "How data Deaths look on Map")
```


How data moving on US map
```{r}
# us_covid_Confirmed1<-filter(us_covid_Confirmed,total>0)%>%filter(Long_!=0)
# us_covid_Confirmed1<-arrange(us_covid_Confirmed1,Lat,Long_,dateRep)%>%group_by(Lat,Long_)%>%mutate(time_diff = c(NA,diff(dateRep)))
# check<-filter(us_covid_Confirmed1,time_diff>1)
# 
# 
#   for (i in 1: nrow(check)) {
#     for (j in 1: check$time_diff[i]-1)
#     {
#         newrow<-check[i,]
#         newrow$dateRep<-newrow$dateRep-j
#         us_covid_Confirmed1<-rbind(us_covid_Confirmed1,newrow)
#     }
#   
#   }
# 
#  p<- qmplot(Long_, Lat, data = us_covid_Confirmed1, colour = I('red'), size = I(0.5), darken = .1,source="osm")+labs(title = 'Day: {frame_time}')   + transition_time(us_covid_Confirmed1$dateRep) +  ease_aes('linear')
#   animate(p, fps=3,height = 800, width =800)
```


How Data moving in us map deaths


```{r}
# us_covid_deaths<-filter(us_covid_deaths,total>0)
#   
# p <- qmplot(Long, Lat, data = us_covid_deaths, colour = I('red'), size = I(0), darken = .1,source="osm")+labs(title = 'Day: {frame_time}')   + transition_time(us_covid_deaths$dateRep) +  ease_aes('linear')
#   animate(p, nframes = 200, fps=3)
  
```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
